---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = TRUE
)
```

# poddr

<!-- badges: start -->
[![R build status](https://github.com/jemus42/poddr/workflows/R-CMD-check/badge.svg)](https://github.com/jemus42/poddr/actions)
<!-- badges: end -->

The goal of poddr is to collect podcast data so I can display it at [podcasts.jemu.name](https://podcasts.jemu.name/). It's not intended to be a real package for real people.

## Installation

You can install the released version of poddr from here with:

``` r
remotes::install_github("jemus42/poddr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r setup}
library(dplyr, warn.conflicts = FALSE)
library(poddr)
```

### The Incomparable

```{r incomparable}
incomparable_shows <- incomparable_get_shows()
incomparable_shows

incomparable_episodes <- incomparable_shows %>%
  filter(show %in% c("Unjustly Maligned", "A Legitimate Salvage")) %>%
  incomparable_get_episodes()

incomparable_episodes
```


### Relay.fm

```{r relay}
relay_shows <- relay_get_shows()
relay_shows

relay_episodes <- relay_shows %>%
  filter(show %in% c("The Prompt", "Connected")) %>%
  relay_get_episodes()

relay_episodes
```


### ATP

Only get the first page (5 episodes)

```{r atp}
atp <- atp_get_episodes(page_limit = 1)
atp
```

### For all the nice people

```{r gathering}
incomparable_episodes %>%
  gather_people() %>%
  select(show, number, person, role)

relay_episodes %>%
  gather_people(people_cols = "host") %>%
  select(show, number, person)
```
