---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = TRUE
)
```

# poddr

<!-- badges: start -->
[![R-CMD-check](https://github.com/jemus42/poddr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jemus42/poddr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of poddr is to scrape episode metadata from The Incomparable,
relay.fm, and ATP and feed it to [podcasts.jemu.name](https://podcasts.jemu.name/).
It's a personal project — not aimed at a wider audience — but the code
is open in case anyone wants to peek under the hood.

## Installation

``` r
pak::pak("jemus42/poddr")
```

## How it works

Each podcast source has a small family of functions: one to list the
shows, one to fetch episodes for a given show (or show list), and a few
parsers exposed for direct use. All network requests go through a
single internal helper that handles per-host throttling, retries on
transient failures, and on-disk HTTP caching, so repeated calls and
scheduled runs don't hammer upstream servers.

```{r setup}
library(dplyr, warn.conflicts = FALSE)
library(poddr)
```

### The Incomparable

```{r incomparable}
incomparable_shows <- incomparable_get_shows()
incomparable_shows

incomparable_get_episodes(
  incomparable_shows |> filter(show == "Unjustly Maligned")
)
```

### relay.fm

```{r relay}
relay_shows <- relay_get_shows()
relay_shows

relay_get_episodes(relay_shows |> filter(show == "Connected"))
```

### ATP

```{r atp}
atp <- atp_get_episodes(page_limit = 1)
atp |>
  tidyr::unnest(links) |>
  select(number, title, link_text, link_url, link_type)
```

### Caching what you fetched

The orchestrators return tibbles and don't touch disk. If you want
RDS/CSV files written to a directory, call `cache_podcast_data()`
explicitly:

```{r cache, eval = FALSE}
atp |> cache_podcast_data(dir = "data_cache", filename = "atp", csv = TRUE)
```

`update_cached_data()` is a convenience that fetches everything and
writes everything; it's what the scheduled GitHub Action uses.

### Per-person view

```{r people}
relay_get_episodes(relay_shows |> filter(show == "Connected")) |>
  gather_people() |>
  select(show, number, person, role)
```
